\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-04 manuscript.Rmd
Delete manuscript_files/figure-latex directory

```{r include=FALSE}
data <- readRDS("leba_2021-09-03.rds")
sem.data <- data[, 6:53] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

#renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam

#Separating the EFA and CFA sample
EFA.data <- sem.data[1:428, ]
CFA.data <- sem.data[429:690,]

@@

#for ( i in 1:length (EFA.data)){numeric <- is.numeric(i) print(numeric)}

shapiro.test(EFA.data$item1)

@@

# Calulating the percentange of correlations higher than .30

@@

```{r factor_identification, eval=FALSE, include=FALSE}

@@

```{r facid, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.png')

>>>>

```{r preparingData, include=FALSE}
data <- readRDS("leba_2021-09-03.rds")

# Separating EFA and CFA samples with descriptive column
descriptives.data <- data

## Merge "0"s and "1"s into "1"s 9select,subset assign)
descriptives.data[ , 6:53 ][ descriptives.data[ , 6:53 ] == 0 ] <- 1
EFA.descriptives <- descriptives.data[1:428,]
CFA.descriptives <- descriptives.data[429:690, ]

#Separating the EFA and CFA(only items)
sem.data <- data[, 6:53] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam

### EFA data
EFA.data <- sem.data[1:428, ]

### CFA Data
CFA.data <- sem.data[429:690,]
CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
CFA.data <- CFA.data %>% 
  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37)

### IRT data
IRT.data <- sem.data
IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
IRTRitem37 = recode(IRT.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
IRT.data <- IRT.data %>% 
  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
```

```{r descriptives, eval=FALSE, include=FALSE}
#Use these  data frames for descriptive
EFA.descriptives #Only EFA
CFA.descriptives #Only CFA

@@

@@

# Calculating the percentange of correlations higher than .30

@@

```{r factor_identification, include=FALSE}

@@

```{r facid, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.jpeg')
